---
title: "Data Collection using API and Web Scraping"
author: "Ouatatchin Kone"
output: html_document
---


## Executive Summary

This data collection project consists of two mini-projects using API and Web Scraping.

In the first mini-project, I use API technique to collect job-based data from Job postings portals and stored in IBM cloud in order to identify trends on emerging programming languages and database skills.

In the second mini-project, I use Web Scraping technique to collect Amazon 30 desktop best sellers. 


## Data Collection from IBM using API

```{r}
library(httr)
library(jsonlite)
library(readr)
library(data.table)
library(tidyverse)
```

Creating a GET response to call the API


```{r Creating a GET response to call the API}
emerging_skills <- GET("https://cf-courses-data.s3.us.cloud-object-storage.appdomain.cloud/IBM-DA0321EN-SkillsNetwork/labs/module%201/Accessing%20Data%20Using%20APIs/jobs.json")
```

Viewing API GET response result

```{r Viewing API GET response result}
str(emerging_skills)
```

Viewing the main source of the data needed from the API 

```{r Viewing the main source of the data needed from the API}
str(emerging_skills$content)
```

Converting the raw data to text

```{r Converting the raw data to text}
emerging_skills_content <- content(emerging_skills, "text")
str(emerging_skills_content)
```
emerging_skills_JSON <- fromJSON(emerging_skills_content)




## Data Collection from Amazon using Web Scraping

```{r}
library(robotstxt)

library(rvest)

library(selectr)

library(xml2)

library(dplyr)

library(stringr)

library(forcats)

library(magrittr)

library(tidyr)

library(lubridate)

library(tibble)

library(purrr)
```

Checking whether we are allowed to access the website 

```{r Checking whether we are allowed to access the website}
paths_allowed(
  
  paths = c ("https://www.amazon.com/Best-Sellers-Desktop-Computers/zgbs/electronics/565098"))
```

Reading html

```{r Reading html}
top_computers <- read_html("https://www.amazon.com/Best-Sellers-Desktop-Computers/zgbs/electronics/565098")
top_computers
```

Extracting computer names

```{r Extracting computer names}
top_computers %>%
  html_nodes("._cDEzb_p13n-sc-css-line-clamp-3_g3dy1") %>%
  html_text() %>%
  str_split(',') %>%
  map_chr(1) -> Brand_name
Brand_name
```

Extracting computer prices

```{r Extracting computer prices}
top_computers %>%
  html_nodes(".a-link-normal span") %>%
  html_text() %>%
  str_extract(pattern = "^\\$.*") %>%
  na.omit() %>%
  unique() -> Price
Price
```

Extracting computer ratings

```{r Extracting computer ratings}
top_computers %>%
  html_nodes(".a-icon-alt") %>%
  html_text() %>%
  str_split('out') %>%
  map_chr(1) %>%
  str_trim()-> Rating
Rating
```

Merging data frames into one data frame named Amazon_Computer_Best_Sellers

```{r Merging data frames into one data frame}
Amazon_Computer_Best_Sellers <- tibble(Brand_name, Price, Rating)
Amazon_Computer_Best_Sellers
```

